Goes Here

### 2012-07-30 paper.tex
some citation

[20] built a system

@@

simulation method for the appearance of translucent materials [59]. 

@@

and the use of pre-computation, similar to pre-computed light transport approaches [63].

@@

of modeling and simulating soft materials and their deformation behavior [22, 60].

@@

In order to measure viscoelastic material properties, we will need to modify our current measurement
system and procedures. We will use repeatable, time-coded measurements to estimate
Figure 5: From left to right: Force-and-deformation capture of a non-linear heterogeneous pillow;
synthesized deformation with fitted material parameters; and interactive deformation synthesized
with our soft tissue modeling technique using scattered data interpolation [60].

@@

manager.loadMaterialLibrary("material_file");
manager.setGenerator(new HeightFieldGenerator());
manager.setSimulator(new SomeColorSimulator());
manager.setMetric(new SomeColorMetric());

@@

  new SimulatedAnealing/GradientDescent());

@@

To generate BRDF
\begin{verbatim}
manager.setGenerator(new StackingGenerator());
manager.setSimulator(new BRDFSimulator());
manager.setMetric(new SomeImageMetric());
Shape shape("filename"), 
Image goal("filename1");
\end{verbatim}

Deformation
\begin{verbatim}
scene.addForce(new Force(pos, dir, shapeID));
scene.addConstraint(
  new Constraint(
    FIX_VERTEX, vertexList, shapeID));
Shape goal;
manager.setSimulator(new FEMSimulator());
\end{verbatim}

\section{Experiments}
\subsection{Previous Work}
Subsurface scattering. Mechanical properties
\begin{figure}
\begin{subfigure}[b]{0.3\textwidth}
	\centering
% 	\includegraphics[width=\textwidth]{a}
   	\caption{}
    \label{fig:ssOrigin}
    \end{subfigure}
    ~ 
    \begin{subfigure}[b]{0.3\textwidth}
    \centering
%  	\includegraphics[width=\textwidth]{a}
    \caption{}
    \label{fig:ssPrint}
\end{subfigure}
\caption{Subsurface Scattering. (a)Original object. (b)Printed model.}
\label{fig:SS}
\end{figure}

@@

\bibliographystyle{acmsiggraph}
\bibliography{template}
\end{document}

>>>>

\cite{Matusik:2009} built a system

@@

simulation method for the appearance of translucent materials \cite{Hasan:2010}. 

@@

and the use of pre-computation, similar to pre-computed light transport approaches \cite{Sloan:2002}.

@@

of modeling and simulating soft materials and their deformation behavior \cite{Bickel:2010,Bickel:2009}.

@@

In order to measure viscoelastic material properties, we will need to modify our current measurement
system and procedures. We will use repeatable, time-coded measurements to estimate
Figure 5: From left to right: Force-and-deformation capture of a non-linear heterogeneous pillow;
synthesized deformation with fitted material parameters; and interactive deformation synthesized
with our soft tissue modeling technique using scattered data interpolation \cite{Bickel:2010}.

@@

manager.loadMaterialLib("material_file");
manager.setGenerator(
  new HeightFieldGenerator());
manager.setSimulator(colorSimulator());
manager.setMetric(someColorMetric());

@@

  simulatedAnealing);
  //or e.g. gradientDescent

@@

To generate BRDF
\begin{verbatim}
manager.setGenerator(stackingGenerator);
manager.setSimulator(brdfSimulator);
manager.setMetric(someImageMetric);
Shape shape("filename"), 
Image goal("filename1");
\end{verbatim}

Deformation
\begin{verbatim}
force = new Force(pos, dir, shapeID);
constraint = new Constraint(
    FIX_VERTEX, vertexList, shapeID));

scene.addForce(force);
scene.addConstraint(constraint);
Shape goal;
manager.setSimulator(femSimulator);
\end{verbatim}

\section{Experiments}
\subsection{Previous Work}
Subsurface scattering. Mechanical properties
\begin{figure}
\begin{subfigure}[b]{0.3\textwidth}
	\centering
 %	\includegraphics[width=\textwidth]{Spec2FabData.png}
   	\caption{}
    \label{fig:ssOrigin}
    \end{subfigure}
    ~ 
    \begin{subfigure}[b]{0.3\textwidth}
    \centering
%  	\includegraphics[width=\textwidth]{a}
    \caption{b}
    \label{fig:ssPrint}
\end{subfigure}
\caption{Subsurface Scattering. (a)Original object. (b)Printed model.}
\label{fig:SS}
\end{figure}

@@

\bibliographystyle{acmsiggraph}
\bibliography{paper}
\end{document}
